GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-23 paper/paper.tex
add AAI.bib

\section{Background and Related Work}

@@

\section{RELATED WORK}
Survey the most important recommendation system, we have a few conclusions.
Traditionally, recommender systems are usually classified into the following three categories: 
1. User-based Collaborative Filtering Systems[Reference 1篇]:
The user will be recommended items similar to the ones the user preferred in the past.
2. Item-based Collaborative Filtering Systems[Reference 3篇]:
The user will be recommended items that people with similar tastes and preferences liked in the past.
3. Hybrid Recommender Systems[Reference 2篇]:
These methods combine the above two methods.
They usually suggest books, music albums, from a set of input parameters, possibly including user profiles, purchase history, etc.

>>>>

\section{Related Work}
Traditionally, recommender systems are classified into the following three categories: 
1. User-based Collaborative Filtering Systems~\cite{Herlocker}:
The user will be recommended items similar to the ones the user preferred in the past.
2. Item-based Collaborative Filtering Systems~\cite{Sarwar, Linden}:
The user will be recommended items that people with similar tastes and preferences liked in the past.
3. Hybrid Recommender Systems[Reference 2篇]:
These methods combine the above two methods.
They usually suggest books, music albums, from a set of input parameters, possibly including user profiles, purchase history, etc.

@@
